Kepler's Demographic Cliff: Ages of Young Stars and Planets in the Kepler Field

### 2024-04-28 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Kepler's demographic cliff,} visible in the
		rotation-derived age distribution of stars (left) and planet hosts
		(right) in the Kepler field.
		The
		light gray histogram does not impose any requires on factors such as
		binarity, crowding, or the star's evolutionary state;
		the age calculation was more likely to be valid for stars that meet the criteria
		discussed in Section~\ref{subsec:flags} (black).
		\label{fig:hist_tgyro}
	}
\end{figure*}

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{hist_samples_koi_gyro_ages_hist_field_gyro_ages_20240405_maxage3200.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Kepler's demographic cliff,} visible in the
		rotation-derived ages of stars (left) and planet hosts
		(right) in the Kepler field.
		The 
		light gray histograms correspond to all
		\nuniqstarsantosrotteffcut\
		$T_{\rm eff}\in[3800,6200]\,$K Kepler stars with reported
		rotation periods, and all 
		\nplhoststarwgyroage\ planet-hosting stars with reported
		rotation periods.
		The black histograms impose necessary quality cuts
		on factors such as
		binarity, crowding, and the star's evolutionary state
		( Section~\ref{subsec:flags}).
		In detail, these ``histograms'' are resampled from the posterior
		probability distributions.
		{\bf todo: numbers dont match.  why?}
		\label{fig:hist_tgyro}
	}
\end{figure*}
